A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-15 dl-paper.tex
Minor fix

Notice that $\KO_2(2n, R) = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R))$ is different from $\K_2(\rD_n, R) = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))$. The relationship between these groups is illustrated by the exact sequence
\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} by means of the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R)$ is isomorphic to the group $K_3^{G, P}$ in which $G = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $P = \mathrm{Epin}(2n, -)$ is its elementary subfunctor.

>>>>

Now set $\widetilde{G}_n = G(\rD_n, -) = \mathrm{Spin}(2n, -)$ and $\widetilde{P}_n = \mathrm{E}(\rD_n, -) = \mathrm{Epin}(2n, -)$.
Notice that for $n\geq 3$ the groups
\begin{align*}
   \KO_2(2n, R) &= \K_2^{G_n,P_n} = \Ker(\St(\rD_n, R) \to \mathrm{SO}(2n, R)), \\
 \K_2(\rD_n, R) &= \K_2^{\widetilde{G}_n,\widetilde{P}_n} = \Ker(\St(\rD_n, R) \to \mathrm{Spin}(2n, R))
\end{align*}
are related via the exact sequence
\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
which can be obtained from the exact sequence on p.~189 of~\cite{Ba74} using the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong K_3^{\widetilde{G}_n, \widetilde{P}_n}$.
